Estimating the number of clusters using Cross Validation

### 2015-06-10 cvclust.tex
Typo correction

Our proposed method is a complete data-driven approach which doesn't rely on any parametric assumptions. Trough novel form of partitioning data set, we are able to employing the cross-validation procedure in clustering exactly the same way as in supervised learning problem. Hence, it's easy for reader to understand the intuition behind our proposed method. Simulation and real data application shows the superior performance of our proposed method compare with existing methods in high-dimension settings and heavy-tailed data. Since the embedded cross-validation procedure is well understood, it also makes our method potentially easily to be extended in future study.

>>>>

Our proposed method is a complete data-driven approach which doesn't rely on any parametric assumptions. Through novel form of partitioning data set, we are able to employing the cross-validation procedure in clustering exactly the same way as in supervised learning problem. Hence, it's easy for reader to understand the intuition behind our proposed method. Simulation and real data application shows the superior performance of our proposed method compare with existing methods in high-dimension settings and heavy-tailed data. Since the embedded cross-validation procedure is well understood, it also makes our method potentially easily to be extended in future study.
